---
title: "Scraping Spotify"
author: "Jorge Argueta (from Datacritics by Jake Daniels)"
date: "10/7/2018"
output: html_document
---

Remove Objects from Environment
```{r}
ls()
rm(list = ls())
```

```{r}
suppressMessages(library(rvest))
suppressMessages(library(rvest))
suppressMessages(library(tidyverse))
suppressMessages(library(tidyverse))
suppressMessages(library(magrittr))
suppressMessages(library(scales))
suppressMessages(library(knitr))
suppressMessages(library(lubridate))
```

These are the websites where we are going to scrape the data:

Top 200 hits on Spotify from the CANADA, February 2018

Constant -----------------------------------/Variable
https://spotifycharts.com/regional/ca/daily/2018-03-31



1. Fix the Constant, this is only for Canada
```{r}
url <- "https://spotifycharts.com/regional/ca/daily/"
```

2. Define the Range for Our Variable
```{r}
timevalues <- seq(as.Date("2018/10/01"), as.Date("2018/12/04"), by = "day")
glimpse(timevalues)
str(timevalues)
```

3. Uniting the Two
```{r}
unitedata<- function(x){
 full_url <- paste0(url, x)
 full_url
}
finalurl <- unitedata(timevalues)

head(finalurl)
```

Shopping for Attributes with SelectorGadget(use goolge CHROME and make it an extension)
```{r}
SpotifyScrape <- function(x){
 page <- x
 rank <- page %>% read_html() %>% html_nodes('.chart-table-position') %>% html_text() %>% as.data.frame()
 track <- page %>% read_html() %>% html_nodes('strong') %>% html_text() %>% as.data.frame()
 artist <- page %>% read_html() %>% html_nodes('.chart-table-track span') %>% html_text() %>% as.data.frame()
 streams <- page %>% read_html() %>% html_nodes('td.chart-table-streams') %>% html_text() %>% as.data.frame()
 dates <- page %>% read_html() %>% html_nodes('.responsive-select~ .responsive-select+ .responsive-select .responsive-select-value') %>% html_text() %>% as.data.frame()

#combine, name, and make it a tibble
 chart <- cbind(rank, track, artist, streams, dates)
 names(chart) <- c("Rank", "Track", "Artist", "Streams", "Date")
 chart <- as.tibble(chart)
 return(chart)
}
```

This step will take a couple or minutes...
```{r}
spotify <- map_df(finalurl, SpotifyScrape)
```

```{r}
glimpse(spotify)
View(spotify)
```

Cleaning the Pull
```{r}
spotify %<>% 
  mutate( Artist = gsub("by ", "", Artist), 
          Streams = gsub(",", "", Streams), 
          Streams = as.numeric(Streams), 
          Date = as.Date(spotify$Date, "%m/%d/%Y")
          )

# Hint: mutate(Artist = gsub("by ",....) , Streams = gsub(",",...)) 
# and then look at the column structures and correct them accordingly.
```

```{r}
head(spotify)
```

Create a flag for CA
```{r}
max_row<-NROW(spotify)
list1<- 1:max_row
Country <- rep("Canada",length(list1))
spotify2 <- cbind(spotify, Country)
head(spotify2)
```

```{r}
# Saving object to a file.
saveRDS(spotify2, file = "spotify_CA_12052018.rds")
# Write CSV in R
write.csv(spotify2, file = "spotify_CA_12052018.csv")
```

